---
title: "How to use and cite popprxl"
author: "Zhian N. Kamvar and Niklaus J. Grünwald"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use and cite popprxl}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Citing popprxl

This package is a wrapper for [*poppr*](https://cran.r-project.org/package=poppr)
and [*readxl*](https://cran.r-project.org/package=readxl). When using this
package, please cite the *poppr* package:

```{r poppr_citation}
citation(package = "poppr")
```


# Using popprxl

There is only one function in popprxl: `read.genalexcel()`. This allows you to
read [GenAlEx](http://biology-assets.anu.edu.au/GenAlEx/Welcome.html) formatted
excel files in *.xlsx* or *.xls* format.

Here's an example using the `nancycats` data set from the
[*adegenet*](https://cran.r-project.org/package=adegenet) package.

> Note: The `system.file()` command is a way to access files that come with a
> package. You will need to supply the path to your own excel file.

```{r load_cats}
library("popprxl")
(nancyxlsx <- system.file("files/nancycats.xlsx", package = "popprxl"))
(nancy    <- read.genalexcel(nancyxlsx))
```

Because *poppr* is loaded along with *popprxl*, you can use any functions in
*poppr*:

```{r missing_cats, fig.width = 8, fig.height = 5}
info_table(nancy, plot = TRUE)
```




